---
title: "A Comparison of Reproducible Tools"
classoption: landscape
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(magrittr)
```

Below is a table of project management tools for R, along with the meaning of the acronyms that we used.

## Comparison of Project Management Tools

```{r}
dt1 <- read.csv("comparison.csv", stringsAsFactors = FALSE)
kableExtra::kable(dt1) %>% kableExtra::row_spec(0,bold=TRUE) %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```


### Deployment Strategy

* VE  = Virtual Environment
* CI  = Container Image
* OS  = Other Strategy

### Other Features

* PM  = Project Management
* CLI = Command Line Interface
* RP  = R Package


### Primary Features

* PPM = Proprietary Package Manager
* PRI = Proprietary R Installation
* PR  = Proprietary Repository
* PRM = Proprietary Repository Manager
* PST = Proprietary Suite of Tools
* NPM = Native Package Manager
* NRI = Native R Installation
* NR  = Native Repository
* NRM = Native Repository Manager
* NST = Native Suite of Tools
* OF  = Other Feature(s)




